---
title: "popthemes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height = 2,
  fig.width = 3
)
```




<!-- badges: start -->


<!-- badges: end -->

## What?

This is a collection of colour palettes based on 90s pop album covers.

Some of these appeared frequently in web searches, so they must be good.

Featuring: 

- Aqua 
- Bangles
- Beck
- Betty Boo
- Breeders
- B*Witched
- Deee Lite
- Hole
- No Doubt
- S Club 7
- Spice Girls
- Steps

## Why?

Because[I've done Metallica](https://github.com/johnmackintosh/metallicaRt) and [classic rock](https://github.com/johnmackintosh/rockthemes).

Although rockthemes has some pop acts in it as well, including No Doubt and DeeeLite, who also appear here. Don't worry about it.


## Installation

This will probably not go to CRAN, so please install using the remotes package.

```{r message=FALSE, warning=FALSE}
#library(remotes)
#remotes::install_github("johnmackintosh/popthemes")
library(popthemes)
```

# Palettes and Themes


```{r aqua, fig.show = "hold",out.width = "33%"}
pop_palette("aqua")
pop_palette("bangles")
pop_palette("beck")
```



```{r boo, fig.show = "hold",out.width = "33%"}
pop_palette("boo")
pop_palette("breeders")
pop_palette("bwitched")
```



```{r deeelite, fig.show = "hold",out.width = "33%"}
pop_palette("deeelite")
pop_palette("hole")
pop_palette("nodoubt")
```



```{r sclub, fig.show = "hold",out.width = "33%"}
pop_palette("sclub7")
pop_palette("spice")
pop_palette("steps")
```



## Credit

[Thanks to Ryo for the tvthemes package](https://github.com/Ryo-N7/tvthemes) which helped me get this off the ground quickly


## Code of Conduct

Please note that the popthemes project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this
project you agree to abide by its terms. 



## Contributing

See the [Contribution guide](.github/CONTRIBUTING.md)
